paper3

### 2022-07-11 paper3.Rmd
update Hyperopt

-   `eta` [0,1] is analogous to learning rate in GBM conceived as the step size shrinkage.

-   `n_estimators` [X/L/C]: no. of boosting iterations

-   `gamma` [0,∞] specifies the minimum loss reduction required to make a split.

-   `max_depth` [0,∞] refers to the maximum depth of a tree, same as GBM, which is used to control over-fitting as higher depth will allow model to learn relations very specific to a particular sample.

-   `min_child_weight` [0,∞] is similar to min_child_leaf in GBM but not exactly which refers to min 'sum of weights' of observations while GBM has min 'number of observations.'

-   `max_delta_step` [0,∞] is usually not needed, but it might help in logistic regression when class is extremely imbalanced.

-   `subsample` [0,1] denotes the fraction of observations to be randomly samples for each tree.

-   `colsample_bytree`

-   `lamda` denotes L2 regularization term on weights (analogous to Ridge regression).

-   `alpha` denotes L1 regularization term on weights (analogous to Lasso regression), which can be used in case of very high dimensionality so that the algorithm runs faster when implemented.

-   `tree_method`

-   `scale_pos_weight`

-   `max_leaves`

```{python}
#%time
from hyperopt import fmin, tpe, hp, STATUS_OK, Trials, space_eval
import numpy as np

# configuration spaces/structures using dictionary container type
param_space = {
  # General Parameters
           'booster': 'gbtree',
     # 'boosting_type': hp.choice('boosting_type', ['gbdt', 'dart']),
     #     'verbosity':
     #       'nthread':

  # Booster Parameters      
               'eta': hp.uniform('eta', 0.01, 1.01),
             'gamma': hp.quniform('gamma', 0.1, 5, 0.05), 
         'max_depth': hp.choice('max_depth', np.arange(1, 30, 1, dtype=int)),
  'min_child_weight': hp.choice('min_child_weight', np.arange(1, 30, 1, dtype=int)),     
         'subsample': hp.quniform('subsample', 0.3, 1.01, 0.05),
  'colsample_bytree': hp.uniform('colsample_bytree', 0.5, 1.0),
             'lamda': hp.uniform('lambda', 0.0, 1.0),
             'alpha': hp.quniform('alpha', 40, 180, 1),
  #      'tree_method': 
  # 'scale_pos_weight':
  #       'max_leaves':

      # 'n_estimators': hp.quniform('n_estimators', 5, 35, 1),
        # 'num_leaves': hp.quniform('num_leaves', 5, 50, 1),

  # Learning Task Parameters  
         'objective': 'multi:softmax',
       'eval_metric': 'mlogloss',
              'seed': 2046
    }

# Sample values from these configuration spaces using the routines in hyperopt.pyll.stochastic
from hyperopt.pyll.stochastic import sample
space = {'learning_rate': hp.loguniform('learning_rate', np.log(0.01), np.log(1))}
print(sample(space))
```

#### 2. Define an objective function

@@

```{python}
import xgboost as xgb
from sklearn.metrics import cohen_kappa_score
from hyperopt import fmin, tpe, hp, STATUS_OK, Trials, space_eval

# https://notebooks.githubusercontent.com/view/ipynb?browser=chrome&color_mode=auto&commit=daa2504c337a74778632d44834209425cb6d357f&device=unknown&enc_url=68747470733a2f2f7261772e67697468756275736572636f6e74656e742e636f6d2f4d696c6164536861686964692f46726175642d446574656374696f6e2d5847426f6f73742f646161323530346333333761373437373836333264343438333432303934323563623664333537662f5847426f6f73745f46726175645f446574656374696f6e2e6970796e62&logged_in=false&nwo=MiladShahidi%2FFraud-Detection-XGBoost&path=XGBoost_Fraud_Detection.ipynb&platform=android&repository_id=152300978&repository_type=Repository&version=98
def objective(params, X_train = X_train, y_train = y_train, X_test = X_test, y_test = y_test):

    model = xgb.XGBClassifier(params,
                              eval_metric = "rmse", 
                              n_estimators = 2000)

    model.fit(X_train, y_train)

    y_pred = model.predict(X_test)
    score = np.mean(cohen_kappa_score(y_test, y_pred))

    return {'loss': score, 'status': STATUS_OK}

@@

#### 3. Minimize the objective over the space

It is the method used to construct the surrogate objective function and choose the next values to evaluate.

@@

```{python}
from hyperopt import fmin, tpe

trials = Trials()
best = fmin(fn = objective,
            space = param_space,
            algo = tpe.suggest, 
            max_evals = 10)

print(best)
```

```{python}
tune_xgb(param_space, X_train, y_train, 100, 100, 100)
```

```{python}
trials = Trials()
best = fmin(fn=hyperparameter_tuning,
            space=space,
            algo=tpe.suggest,
            max_evals=100,
            trials=trials)

print (best)

Tuning hyper-parameters of the XGBoost classifier using Bayesian Optimization

if __name__ == "__main__":    
    # Loading the data
    data = pd.read_csv('creditcard.csv')
    X = data.drop('Class', axis = 1)
    y = data['Class']

    # Train/test split, 80/20, random_state set for reproduibility
    X_train, X_test, y_train, y_test = train_test_split(X, y, stratify = y, test_size = 0.2, random_state = 1)

    # Further splitting the initial training set so that 10% of all data(1/8 of 80%) 
    # can be used as the evaluation set by XGBoost for early stopping
    X_train, X_early_stop, y_train, y_early_stop = train_test_split(X_train, y_train, stratify = y_train, test_size = 1/8, random_state = 1)

    # The prior probability distribution of parameters for Bayesian optimization

    param_space = {
  # General Parameters
           'booster': 'gbtree',
     # 'boosting_type': hp.choice('boosting_type', ['gbdt', 'dart']),
     #     'verbosity':
     #       'nthread':

  # Booster Parameters      
               'eta': hp.uniform('eta', 0.01, 1.01),
             'gamma': hp.quniform('gamma', 0.1, 5, 0.05), 
         'max_depth': hp.choice('max_depth', np.arange(1, 30, 1, dtype=int)),
  'min_child_weight': hp.choice('min_child_weight', np.arange(1, 30, 1, dtype=int)),     
         'subsample': hp.quniform('subsample', 0.3, 1.01, 0.05),
  'colsample_bytree': hp.uniform('colsample_bytree', 0.5, 1.0),
             'lamda': hp.uniform('lambda', 0.0, 1.0),
             'alpha': hp.quniform('alpha', 40, 180, 1),
  #      'tree_method': 
  # 'scale_pos_weight':
  #       'max_leaves':

      # 'n_estimators': hp.quniform('n_estimators', 5, 35, 1),
        # 'num_leaves': hp.quniform('num_leaves', 5, 50, 1),

  # Learning Task Parameters  
         'objective': 'multi:softmax',
       'eval_metric': 'mlogloss',
              'seed': 2046
    }

    param_space = {
            'learning_rate': hyperopt.hp.loguniform('learning_rate', np.log(0.01), np.log(0.2)),
            'subsample': hyperopt.hp.uniform('subsample', 0.25, 1),
            'colsample_bytree': hyperopt.hp.uniform('colsample_bytree', 0.7, 1.0),
            'min_child_weight': hyperopt.hp.choice('min_child_weight', [1, 3, 5, 7]),
            'reg_alpha': hyperopt.hp.uniform('reg_alhpa', 0, 1.0),
            # Avoiding lambda = 0. There is a Github issue on strange behaviour with lambda = 0
            'reg_lambda': hyperopt.hp.uniform('reg_lambda', 0.01, 1.0),
            }

      from hyperopt.pyll.stochastic import sample
space = {'subsample': hp.uniform('subsample', 0.25, 1)}
print(sample(space))

      best_params = tune_xgb(param_space, X_train, y_train, X_early_stop, y_early_stop, n_iter = 150)
      print('\tThe best hyper-parameters found:\n')print(*['\t\t%s = %s' % (k, str(round(v, 4))) for k, v in best_params.items()], sep='\n')
```

other references

```{python}
from sklearn.model_selection import cross_val_score
from hyperopt import STATUS_OK
import lightgbm as lgb

def objective_function(params):
    clf = lgb.LGBMClassifier(**params)
    score = cross_val_score(clf, X_train, y_train, cv=5).mean()
    return {'loss': -score, 'status': STATUS_OK}

def score(params):
    model = XGBRegressor(**params)

    model.fit(X_train, Y_train, eval_set=[(X_train, Y_train), (X_valid, Y_valid)],
              verbose=False, early_stopping_rounds=10)
    Y_pred = model.predict(X_valid).clip(0, 20)
    score = sqrt(mean_squared_error(Y_valid, Y_pred))
    print(score)
    return {'loss': score, 'status': STATUS_OK}

def optimize(trials, space):

    best = fmin(score, space, algo=tpe.suggest, max_evals=1000)
    return best

trials = Trials()
best_params = optimize(trials, space)

# Return the best parameters
space_eval(space, best_params)

From Li Ziqi

def score(params, n_folds=5):

    #Cross-validation
    d_train = xgboost.DMatrix(X_coords,y)

    cv_results = xgboost.cv(params, d_train, nfold = n_folds, num_boost_round=500,
                        early_stopping_rounds = 10, metrics = 'rmse', seed = 0)

    loss = min(cv_results['test-rmse-mean'])

    return loss

def optimize(trials, space):

    best = fmin(score, space, algo=tpe.suggest, max_evals=2000,
                rstate=np.random.RandomState(333))#Add seed to fmin function
    return best
```

#### 4. Results

@@

# Leave most parameters as default
param = {'objective': 'multi:softmax',  # Specify multiclass classification
         'num_class': 4,  # Number of possible output classes
         # 'tree_method': 'gpu_hist',  # Use GPU accelerated algorithm
         'eta': 0.451,
         'max_depth': 12,
         'gamma': 0,
         'subsample': 0.758,
         'colsample_bytree': 1,
         'min_child_weight': 0.2,
         'tree_method': 'hist',
         'predictor': 'cpu_predictor'
         }

# Convert input data from numpy to XGBoost format
dtrain = xgb.DMatrix(X_train, label=y_train)
dtest = xgb.DMatrix(X_test, label=y_test)

@@

# Train model
# model = xgb.train(param, dtrain, num_round, evals=[(dtest, 'test')], evals_result=gpu_res)
# print("GPU Training Time: %s seconds" % (str(time.time() - start)))
model = xgb.train(param, dtrain, num_round, evals=[(dtest, 'test')])
print(time.time() - start)

# Evaluate model using test data
from sklearn.metrics import accuracy_score
predictions = model.predict(dtest)
accuracy = accuracy_score(y_test, predictions)
print("Accuracy: %.2f%%" % (accuracy * 100.0))

from sklearn.metrics import cohen_kappa_score
kappa = cohen_kappa_score(y_test, predictions)
print("Kappa: %.2f%%" % (kappa))

# save to JSON
model.save_model("/Users/mac/PycharmProjects/XGBoost/models/model_A.json")
```

>>>>

-   `eta` [0,1] is analogous to learning rate in GBM conceived as the step size shrinkage.
-   `n_estimators` [X/L/C]: no. of boosting iterations
-   `gamma` [0,∞] specifies the minimum loss reduction required to make a split.
-   `max_depth` [0,∞] refers to the maximum depth of a tree, same as GBM, which is used to control over-fitting as higher depth will allow model to learn relations very specific to a particular sample.
-   `min_child_weight` [0,∞] is similar to min_child_leaf in GBM but not exactly which refers to min 'sum of weights' of observations while GBM has min 'number of observations.'
-   `max_delta_step` [0,∞] is usually not needed, but it might help in logistic regression when class is extremely imbalanced.
-   `subsample` [0,1] denotes the fraction of observations to be randomly samples for each tree.
-   `colsample_bytree`
-   `lamda` denotes L2 regularization term on weights (analogous to Ridge regression).
-   `alpha` denotes L1 regularization term on weights (analogous to Lasso regression), which can be used in case of very high dimensionality so that the algorithm runs faster when implemented.
-   `tree_method`
-   `scale_pos_weight`
-   `max_leaves`

```{python}
# -- hyperopt for optimising a 
from hyperopt import fmin, tpe, hp, STATUS_OK, Trials, space_eval
from sklearn.metrics import cohen_kappa_score
import numpy as np
import xgboost as xgb

# -- define a search space
param_space = {
  # General Parameters
           'booster': 'gbtree',
     # 'boosting_type': hp.choice('boosting_type', ['gbdt', 'dart']),
     #     'verbosity':
     #       'nthread':

  # Booster Parameters      
               'eta': hp.uniform('eta', 0.01, 1.01),
             'gamma': hp.quniform('gamma', 0.1, 5, 0.05), 
         'max_depth': hp.choice('max_depth', np.arange(1, 30, 1, dtype=int)),
  'min_child_weight': hp.choice('min_child_weight', np.arange(1, 30, 1, dtype=int)),     
         'subsample': hp.quniform('subsample', 0.3, 1.01, 0.05),
  'colsample_bytree': hp.uniform('colsample_bytree', 0.5, 1.0),
        'reg_lambda': hp.uniform('reg_lambda', 0.0, 1.0),
         'reg_alpha': hp.quniform('reg_alpha', 40, 180, 1),
  #      'tree_method': 'hist','gpu_hist',  # Use GPU accelerated algorithm
  # 'scale_pos_weight':
  #       'max_leaves':
  #     'n_estimators': hp.quniform('n_estimators', 5, 35, 1),
  #       'num_leaves': hp.quniform('num_leaves', 5, 50, 1),
  #        'predictor': 'cpu_predictor'

  # Learning Task Parameters
         'num_class': 4,                   # Number of possible output classes
         'objective': 'multi:softmax',     # Specify multiclass classification
       'eval_metric': 'merror',
              'seed': 2046
    }

# Sample values from these configuration spaces using the routines in hyperopt.pyll.stochastic
# from hyperopt.pyll.stochastic import sample
# space = {'learning_rate': hp.loguniform('learning_rate', np.log(0.01), np.log(1))}
# print(sample(space))
```

#### 2. Define an objective/loss/cost function

@@

```{python}
# -- define an objective function
def objective(params, X_train = X_train, y_train = y_train, X_test = X_test, y_test = y_test):
    model = xgb.XGBClassifier(**params)
    model.fit(X_train, y_train,
              eval_set = [(X_train, y_train), (X_test, y_test)])
    y_pred = model.predict(X_test)
    score = np.mean(cohen_kappa_score(y_test, y_pred))
    # -- return more than just the objective value
    return {'loss': score, 'status': STATUS_OK}
```

@@

#### 3. Minimize the objective over the space (optimisation algorithm)

It is the method used to construct the surrogate objective function and choose the next values to evaluate. The optimization algorithm is based on the Sequential Model-Based Global Optimization (SMBO) methodology with the variants given by the Gaussian Processes (GP), Tree of Parzen Estimators (TPE) and Adaptive Tree of Parzen Estimators (ATPE) algorithms.

@@

```{python}
# -- optimize it using algorithm of choice
def optimize(trials, space):
    best = fmin(fn = objective,
                space = param_space, 
                algo = tpe.suggest,    # the optimisation algorithm
                max_evals = 10,        # the number of iteration
                trials = trials)       # the trials database for fmin
    return best

# -- create a Trials database to store experiment results
trials = Trials()
best_params = optimize(trials, param_space)

# Return the best parameters
space_eval(param_space, best_params)

# -- print out what we got!
# for trial in trials.trials:
#     print(trial)
```
#### 4. Results

@@

# Convert input data from numpy to XGBoost format
dtrain = xgb.DMatrix(X_train, label = y_train)
 dtest = xgb.DMatrix(X_test, label = y_test)

@@

# Train model
# model = xgb.train(param, dtrain, num_round, evals=[(dtest, 'test')], evals_result=gpu_res)
# print("GPU Training Time: %s seconds" % (str(time.time() - start)))

best_params['num_class'] = 4
best_params['objective'] = 'multi:softmax'
best_params['eval_metric'] = 'merror'

model = xgb.train(best_params,
                  dtrain,
                  num_round = 1000)
                  #evals = [(dtrain, 'train'),(dtest, 'test')])

print(time.time() - start)

y_pred = model.predict(dtest)

# Evaluate model using test data
from sklearn.metrics import accuracy_score

accuracy = accuracy_score(y_test, y_pred)
print("Accuracy: %.2f%%" % (accuracy * 100.0))

from sklearn.metrics import cohen_kappa_score
kappa = cohen_kappa_score(y_test, y_pred)
print("Kappa: %.2f%%" % (kappa))

# save to JSON
# model.save_model("/Users/mac/PycharmProjects/XGBoost/models/model_A.json")
```
